---
title: "Coral Tipping Points Presentation"
output: ioslides_presentation

Coral Tipping Points Project README

## Collaborators 
- Michelle Platz: University of South Florida 
- Megan Kramer: University of South Florida
- Christina Brown: University of Central Florida
- Frida Bahja : University of Central Florida

This repository contains scripts/data to assess social-ecological tipping points associated with the Stony Coral Tissue Loss Disease event in the Florida Reef Tract. Through an assessment of social and ecological datasets, we hope to identify correlations and understand tipping point dynamics to answer research questions such as: what is the lag time between an environmental catastrophe and the social response?

Datasets we intend to utilize include: 
-	Twitter data from 2012-present (time of tweet, 2012-2021)
-	Gross sales for 64 economy sectors from 2012-present (Monroe County level, monthly timescale)
-	Unemployment from 2012-present (Monroe County level, monthly timescale)
-	Labor force from 2012-present (Monroe County level, monthly timescale)
-	Coral disease: prevalence percentages and boundary from 2017 - 2019 (FRT-wide, daily) 
-	Reef benthic composition from 2012-present (FRT-wide, yearly) 
-	Major storm events from 2012-present (FRT-wide, event date) 
-	Water temperature from 2012-present (FRT-wide, daily)
-	Degree heating weeks from 2012-present (FRT-wide, weekly)
-	Commercial fisheries landings from 2012-present (Monroe Couty, annual) 
-	Reef fish density and diversity from 2012-present (FRT-wide, monthly) 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

